Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-26 manuscript/supplementaryRW.Rmd
updated LandClim report

We provide 200 samples each for 48 plots and at least 190 samples each
for 117 plots while not simulating 35 plots (see reason for excluded
plots in \"Simulation length and equilibrium criteria\"). These stem
from 10 year periods that overlap partially (for \< 2500 simulation
years) or do not overlap (for 2500 simulation years). The number of
recruits (r.trees) is the sum of individuals that cross the threshold
diameter (7/10 cm) in the 10 year sample period per hectare that have
not already died until the sample year. The recruit's basal area (r.ba)
is the sum of the basal area per hectare of the trees that cross the
diameter threshold that have not already died until the sample year. The
total stand basal area (ba) is the basal area per hectare of all trees
in the stand \> 0 cm diameter at breast height (no lower boundary) at
the sample time per species. We provide the data for both diameter
thresholds, 7 and 10 cm. In over 90 % of the decades no recruitment
takes place.

@@

We use the LandClim version 2.0, which calculates forest dynamics at a
decadal time step. The complete reference resource for the LandClim
model and regeneration module are:

@@

Climate inputs for LandClim are at monthly temporal resolution. We used
monthly climate from the CHELSA dataset provided in the protocol using
temperature and precipitation variables. -during the simulations, we
sampled the climate time series randomly.

@@

We used the soil quality provided to infer the Available Water Holding
Capacity needed in LandClim. We assigned 8 cm for soil quality one and
25 cm for soil quality five and interpolated the values for the other
categories linearly between the two extremes.

@@

We used the altitude and soil information provided in the protocol to
create the different landscapes, one per site. However, each landscape
created per site had no slope, altitude, or aspect variation.

@@

We simulated forest dynamics only considering the 11 species proposed in
the protocol: *Fagus sylvatica, Picea abies, Abies alba, Carpinus
betulus, Tilia cordata, Acer pseudoplatanus, Betula* spp.*, Fraxinus
excelsior, Quercus* spp.*, Alnus glutinosa,* and *Pinus sylvestris.*

@@

We simulate forest dynamics from bare ground for each of the sites. We
prepared landscapes of 250x250m without topographical elevation for each
of the sites. The simulations we run from bare ground to 2000 years and
the samples were taken from the year 2000. On the regeneration module,
we use a background probability of 0.001, a dispersal mode based on the
formulation random asymmetric, and the same establishment probability
for all the species included in the simulation of 0.9.

@@

We estimated the outputs based on a sample of 25 random cells every ten
years from 2000 to 4000 of the simulation for one simulation per site,
providing 200 samples per site.

>>>>

We provide 200 samples each for 48 plots and at least 190 samples each
for 117 plots while not simulating 35 plots (see reason for excluded
plots in "Simulation length and equilibrium criteria"). These stem from
10 year periods that overlap partially (for \< 2500 simulation years) or
do not overlap (for 2500 simulation years). The number of recruits
(r.trees) is the sum of individuals that cross the threshold diameter
(7/10 cm) in the 10 year sample period per hectare that have not already
died until the sample year. The recruit's basal area (r.ba) is the sum
of the basal area per hectare of the trees that cross the diameter
threshold that have not already died until the sample year. The total
stand basal area (ba) is the basal area per hectare of all trees in the
stand \> 0 cm diameter at breast height (no lower boundary) at the
sample time per species. We provide the data for both diameter
thresholds, 7 and 10 cm. In over 90 % of the decades no recruitment
takes place.

@@

We used LandClim version 2.0, which calculates forest dynamics at a
decadal time step. The complete reference resources for the LandClim
model and its regeneration module are:

@@

Climate inputs for LandClim are at monthly temporal resolution. We used
monthly climate from the CHELSA dataset provided in the protocol, using
temperature and precipitation variables. During the simulations, we
randomly sampled the annual climate data from the CHELSA time series.

@@

We used the soil quality provided in the protocol to infer the Available
Water Holding Capacity (WHC) needed in LandClim. We assigned WHC = 8 cm
for soil quality one and WHC = 25 cm for soil quality five, and
interpolated the values for the other categories linearly between these
two extremes.

@@

We used the altitude and soil information provided in the protocol to
create 200 landscapes, one per site. However, each landscape created per
site had no slope, altitude, or aspect variation.

@@

We simulated forest dynamics considering only the 11 species proposed in
the protocol: *Fagus sylvatica, Picea abies, Abies alba, Carpinus
betulus, Tilia cordata, Acer pseudoplatanus, Betula* spp.*, Fraxinus
excelsior, Quercus* spp.*, Alnus glutinosa,* and *Pinus sylvestris.*

@@

We simulated forest dynamics from bare ground for each site, using
patches (pixels) with a size of 20x20 cm^2^. We prepared landscapes of
250x250 m without topographical variation for each site. The simulations
we run from bare ground to 2000 years, and the samples were taken
starting in the year 2000. In the regeneration module, we used (1) a
base seeding probability of 0.001, which defines if seeds are available
due to background seed rain; (2) a dispersal mode based on the
formulation \'random asymmetric\'; and (3) the same establishment
probability of 0.9 for all species included in the simulation of, which
sets the same probability for all the species to regenerate
successfully, provided that the abiotic and light conditions are
suitable for establishment.

@@

We estimated the outputs based on a sample of 25 random cells every ten
years from the simulation years 2010 to 4000 for one simulation per
site, thus providing the required 200 samples per site.
